\documentclass[11pt,a4paper,sans]{moderncv}

% --- ModernCV Theme & Color ---
\moderncvstyle{classic} % Options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{burgundy} % Options: blue, orange, green, red, purple, grey, black

% --- Packages & Geometry ---
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{enumitem}

% --- Personal Data ---
\name{Natalia}{Guerra}
\title{Professional Bilingual Pianist\linebreak \& Keyboardist}
\address{Medellín, Colombia}{Open to Global Relocation}

% Contact information
\email{contact@NataliaGuerraMusic.com}
\phone[mobile]{+57 304 469 0037}
\homepage{NataliaGuerraMusic.com}
\social[instagram]{natiguerra.03}
\social[youtube]{@NataliaGuerraMusic} 

% --- Quote / Executive Summary ---
\quote{Versatile Colombian pianist combining strong classical technique with jazz improvisation. Experienced in high-energy showband performance (150+ repertoire), performing with click tracks/sequences, and adapting to international audiences. Disciplined professional with proven leadership skills and C1 English fluency. \linebreak Ready for immediate embarkation.}

% --- Content ---
\begin{document}

\makecvtitle

\section{Musical Performance Experience}

\cventry{Jan 2025 -- Present}{Keyboardist | Showband Musician}{Ruta 77 Band}{Antioquia, Colombia}{}{
\begin{itemize}
    \item Performing member of a high-energy rock/fusion showband specializing in weddings and corporate events.
    \item \textbf{Repertoire Mastery:} Maintain an active setlist of 150+ covers spanning Pop, Rock, R\&B, Swing, and Fusion.
    \item \textbf{Technical Proficiency:} Performance using Click Tracks and backing sequences; live sound management using Nord Keyboards and Logic Pro.
    \item High-volume performance schedule demonstrating stamina and consistency.
\end{itemize}}

\cventry{2019--2021}{International Musician in Residence}{Cultural Exchange Initiative}{Mersin, Turkey}{}{
\begin{itemize}
    \item Served as a musical ambassador in a cross-cultural environment for two years.
    \item Collaborated with the local Turkish Music Academy, studying quarter-tone scales and sharing cultural musical perspectives within Turkish ensembles.
    \item \textbf{Musical Director:} Led multicultural bands at the Mersin House of Prayer; bridged language barriers through musical improvisation and structured chord charts.
    \item Demonstrated high adaptability to new cultures, languages, and living environments.
\end{itemize}}

\cventry{2015--2023}{Session Pianist \& Worship Leader}{Freelance \& House of Prayer}{Bogotá \& Medellín}{}{
\begin{itemize}
    \item Directed bands for large-scale worship gatherings (Bogotá \& Medellín Houses of Prayer).
    \item Specialized in \textbf{Spontaneous Accompaniment} requiring acute listening skills and instant harmonic adaptation.
    \item Worked as a piano instructor for private students, focusing on theory and technique.
\end{itemize}}

\section{Education \& Training}

\cventry{Classical Piano}{Universidad Francisco José de Caldas}{}{Bogotá}{}{
    Focus: Classical repertoire and technique. Studied under Maestro Carlos García Stan.
}

\cventry{Jazz Piano}{Escuela de Artes Fernando Sor}{}{Bogotá}{}{
    Focus: Jazz harmony, improvisation, and ensemble performance. Studied under Maestro Néstor Vivas.
}

\cventry{Colombian Music}{Universidad Distrital -- Academia Luis A. Calvo}{}{Bogotá}{}{
    Focus: Traditional Colombian musical studies and rhythms. Studied under Vanesa Rodríguez.
}

\section{Technical Skills \& Equipment}

\cvitem{Instruments}{\textbf{Nord Keyboards} (Stage/Piano), Acoustic Piano, MIDI Controllers.}
\cvitem{Software}{\textbf{Logic Pro X} DAW Production workflow.}
\cvitem{Performance}{Playing to Click/Backing Tracks, Chart Reading, Memorization, Improvisation.}
\cvitem{Genres}{Classical (University trained), Jazz, Pop/Rock, Fusion, CCM/Worship.}

\section{Professional Reliability \& Leadership}

\cventry{2023--Present}{Team Lead | Discovery Unit}{Redmond Law Firm (New York based)}{Remote}{}{
    \begin{itemize}
        \item Lead a cross-cultural, international team of 7 professionals for a NY Personal Injury firm.
        \item Manages strict deadlines, handles complex logistics, and maintains C1 English fluency in a high-stakes professional environment.
    \end{itemize}
}

\section{Languages \& Documentation}
\cvitemwithcomment{Spanish}{Native Speaker}{}
\cvitemwithcomment{English}{Advanced / Fluent (C1 Equivalent)}{Daily professional use in NY Law firm context}
\cvitemwithcomment{Passport}{Valid Colombian Passport}{Ready for Visa Processing}

\end{document}
